Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-07-22 Optimization - Journal of Climate/template.tex
Addition of the resulting parameters.

The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table_params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. \citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances. The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential heights. To cope with seasonal effects, candidate data are extracted for every year from the archive within a period of 4 months centred around the target date.

@@

The other most know method adds a second level of analogy on humidity variables (Table \ref{table_params_R2}). The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of the reference method on the atmospheric circulation.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
			\hline 
			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& geopotential hgt 500~hPa & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table_params_R1}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of the reference method with humidity variables.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Analogues nb} \\ 
			\hline 
			preselection & \multicolumn{4}{c}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & geopotential hgt 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& geopotential hgt 500~hPa & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & precipitable water * relative humidity 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
			& precipitable water * relative humidity 850~hPa & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table_params_R2}
\end{table}

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.3cm]{figure_map.pdf}}
	\caption{Location of the alpine Rhône catchment in Switzerland. (source: Swisstopo)}
	\label{figure_map}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=10.3cm]{figure_structure_gas.pdf}}
	\caption{Genetic algorithms operational flowchart}
	\label{figure_structure_gas}
\end{figure}

>>>>

The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. \citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances. The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential heights. To cope with seasonal effects, candidate data are extracted for every year from the archive within a period of 4 months centred around the target date.

@@

The other most know method adds a second level of analogy on humidity variables (Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).

@@

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of the reference method on the atmospheric circulation.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			preselection & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{50} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_R1}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of the reference method with humidity variables.}
	\begin{center}
		\begin{tabular}{ccccc}
			\hline \textbf{Level} & \textbf{Variable} & \textbf{Hour} & \textbf{Criteria} & \textbf{Nb} \\ 
			\hline 
			preselection & \multicolumn{4}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{2}{*}{1} & Z 1000~hPa & 12~h & \multirow{2}{*}{S1} & \multirow{2}{*}{70} \\
			& Z 500~hPa & 24~h & & \\ 
			\hline
			\multirow{2}{*}{2} & TPW * RH 850~hPa & 12~h & \multirow{2}{*}{RMSE} & \multirow{2}{*}{30} \\
			& TPW * RH 850~hPa & 24~h & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_R2}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) optimized for the Chablais region. The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
			\hline 
			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & -2.5 - 15.0 \degree E & \multirow{2}{*}{32\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{28} \\
			& & & 37.5 - 57.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z700} & \multirow{2}{*}{24~h} & 2.5 - 10.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
			& & & 42.5 - 45.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{6~h} & -5.0 - 15.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
			& & & 42.5 - 47.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{22\%} & & \\ 
			& & & 40.0 - 50.0 \degree N & & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_GA_z4}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & Z &   &   &   & Z &   &   & ZZ \\
			2  & Z &   &   &   & Z &   &   & ZZ \\
			3  & Z &   &   &   & Z &   &   & ZZ \\
			4  & Z &   &   &   & Z &   &   & ZZ \\
			5  &   &   & Z &   & Z &   &   & ZZ \\
			6  &   &   & Z &   & Z &   &   & ZZ \\
			7  &   &   & Z &   & Z &   &   & ZZ \\
			8  &   &   & Z &   & Z &   &   & ZZ \\
			9  &   &   & Z &   & Z &   &   & ZZ \\
			10 &   &   &   & Z & Z &   &   & ZZ \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (2 levels), optimized for the Chablais region. The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
			\hline 
			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{8}{*}{1} &  \multirow{2}{*}{Z300} & \multirow{2}{*}{12~h} & 0.0 - 15.0 \degree E & \multirow{2}{*}{23\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
			& & & 42.5 - 55.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{25\%} & & \\ 
			& & & 40.0 - 45.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 10.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
			& & & 42.5 - 47.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{26\%} & & \\ 
			& & & 40.0 - 47.5 \degree N & & & \\ 
			\hline 
			\multirow{4}{*}{2} & TPW & \multirow{2}{*}{12~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{57\%} & \multirow{4}{*}{RMSE} & \multirow{4}{*}{25} \\
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			& TPW & \multirow{2}{*}{24~h} & 5.0 - 10.0 \degree E & \multirow{2}{*}{43\%} & & \\ 
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_GA_z4_hi2}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  & Z &   & Z &   &   & Z &   & Z \\
			2  & Z &   &   &   & Z & Z &   & Z \\
			3  & Z &   &   &   & Z & Z & Z &   \\
			4  &   &   & Z &   & Z & Z &   & Z \\
			5  &   & Z &   &   & Z &   & ZZ &   \\
			6  &   & Z &   &   & Z & Z &   & Z \\
			7  &   & Z &   &   & Z & Z &   & Z \\
			8  &   &   & Z &   & Z &   & ZZ &   \\
			9  &   & Z &   &   & Z & Z & Z &   \\
			10 &   & Z &   &   & Z & Z &   & Z \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi2}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   &   &   &   & HH &   &   &   \\
			2  &   &   &   &   & HH &   &   &   \\
			3  &   &   &   &   & HH &   &   &   \\
			4  &   &   &   & H & H &   &   &   \\
			5  &   &   &   &   & HH &   &   &   \\
			6  &   &   &   & H & H &   &   &   \\
			7  &   &   &   & H & H &   &   &   \\
			8  &   &   &   & H & H &   &   &   \\
			9  &   &   &   & H & H &   &   &   \\
			10 &   &   &   & H & H &   &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi2_H}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Parameters of an analogy on the atmospheric circulation (4 levels) and the humidity index (4 levels), optimized for the Chablais region. The columns are the followings: L = level, V = variable, H = hour, D = domain, W = weight, C = criteria, N = number of analogues.}
	\begin{center}
		\begin{tabular}{ccccccc}
			\hline \textbf{L} & \textbf{V} & \textbf{H} & \textbf{D} & \textbf{W} & \textbf{C} & \textbf{N} \\ 
			\hline 
			0 & \multicolumn{6}{l}{$\pm 60$ days around the target date} \\
			\hline 
			\multirow{8}{*}{1} &  \multirow{2}{*}{Z400} & \multirow{2}{*}{6~h} & -5.0 - 12.5 \degree E & \multirow{2}{*}{20\%} & \multirow{8}{*}{S1} & \multirow{8}{*}{74} \\
			& & & 45.0 - 52.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z500} & \multirow{2}{*}{30~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
			& & & 40.0 - 45.0 \degree N & & & \\ 
			& \multirow{2}{*}{Z850} & \multirow{2}{*}{12~h} & 0.0 - 12.5 \degree E & \multirow{2}{*}{28\%} & & \\ 
			& & & 42.5 - 47.5 \degree N & & & \\ 
			& \multirow{2}{*}{Z1000} & \multirow{2}{*}{30~h} & 0.0 - 20.0 \degree E & \multirow{2}{*}{24\%} & & \\ 
			& & & 40.0 - 47.5 \degree N & & & \\ 
			\hline 
			\multirow{8}{*}{2} & TPW & \multirow{2}{*}{24~h} & 7.5 - 10.0 \degree E & \multirow{2}{*}{27\%} & \multirow{8}{*}{RMSE} & \multirow{8}{*}{25} \\
			& *RH500 & & 45.0 - 47.5 \degree N & & & \\ 
			& TPW & \multirow{2}{*}{12~h} & 5.0 - 7.5 \degree E & \multirow{2}{*}{41\%} & & \\ 
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			& TPW & \multirow{2}{*}{18~h} & 0.0 - 7.5 \degree E & \multirow{2}{*}{19\%} & & \\ 
			& *RH700 & & 45.0 - 47.5 \degree N & & & \\ 
			& TPW & \multirow{2}{*}{24~h} & 2.5 - 15.0 \degree E & \multirow{2}{*}{13\%} & & \\ 
			& *RH850 & & 45.0 - 47.5 \degree N & & & \\ 
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:params_GA_z4_hi4}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   & Z & Z &   &   & Z &   & Z \\
			2  &   & Z &   &   & ZZ &   &   & Z \\
			3  &   & Z &   &   & Z & Z & Z &   \\
			4  &   &   & Z &   & Z & Z &   & Z \\
			5  &   & Z & Z &   &   & Z &   & Z \\
			6  &   & Z & Z &   &   & Z &   & Z \\
			7  &   & Z &   &   & ZZ &   &   & Z \\
			8  &   &   & Z & Z &   & Z &   & Z \\
			9  &   & Z &   &   & Z & Z & Z &   \\
			10 &   & Z & Z &   &   & ZZ &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi4}
\end{table}

\begin{table}[htbp]
	\footnotesize
	\caption{Atmospheric levels automatically selected for the analogy of atmospheric circulation at the different groupments.}
	\begin{center}
		\begin{tabular}{ccccccccc}
			\hline \textbf{ID} & \textbf{300} & \textbf{400} & \textbf{500} & \textbf{600} & \textbf{700} & \textbf{850} & \textbf{925} & \textbf{1000} \\ 
			\hline 
			1  &   &   & H &   & HH & H &   &   \\
			2  &   &   &   & H & HH & H &   &   \\
			3  &   &   &   & H & HHH &   &   &   \\
			4  &   &   &   & HH & HH &   &   &   \\
			5  &   &   &   & HH & HH &   &   &   \\
			6  &   &   &   & HH & H & H &   &   \\
			7  &   &   &   & HH & H & H &   &   \\
			8  &   &   &   & HH & H & H &   &   \\
			9  &   &   & H & H & H & H &   &   \\
			10 &   &   &   & H & HH & H &   &   \\
			\hline 
		\end{tabular} 
	\end{center}
	\label{table:levels_GA_z4_hi4_H}
\end{table}

@@

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.3cm]{figures/figure_map.pdf}}
	\caption{Location of the alpine Rhône catchment in Switzerland. (source: Swisstopo)}
	\label{fig:map}
\end{figure}

\begin{figure}[htb]
	\centerline{\includegraphics[width=8.3cm]{figures/figure_structure_gas.pdf}}
	\caption{Genetic algorithms operational flowchart}
	\label{fig:structure_gas}
\end{figure}

\begin{figure}[htb]
	\centering
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_1.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_2.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_3.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_4.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_5.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_6.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_7.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_8.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_9.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4/Spatial_windows_10.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=3.9cm]{figures/spatial_win_z4/legend.png}
	\end{subfigure}
	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels. The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_z4}
\end{figure}

\begin{figure}[htb]
	\centering
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_1.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_2.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_3.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_4.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_5.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_6.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_7.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_8.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_9.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi2/Spatial_windows_10.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi2/legend.png}
	\end{subfigure}
	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 2 atmospheric levels. The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_z4-hi2}
\end{figure}

\begin{figure}[htb]
	\centering
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_1.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_2.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_3.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_4.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_5.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_6.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_7.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_8.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_9.png}
	\end{subfigure}%
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=4cm]{figures/spatial_win_z4-hi4/Spatial_windows_10.png}
	\end{subfigure}
	\begin{subfigure}{.5\columnwidth}
		\centering
		\includegraphics[width=3.9cm]{figures/spatial_win_z4-hi4/legend.png}
	\end{subfigure}
	\caption{Optimized spatial windows for the analogy of atmospheric circulation on 4 atmospheric levels and the analogy on the humidity index on 4 atmospheric levels. The atmospheric levels are ordered by increasing pressure and increasing time for the same levels.}
	\label{fig:spatial_windows_z4-hi4}
\end{figure}
